SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-11 scipy-1.0/paper.tex
Revision of manuscript PR 37 based on reviewer feedback; added a few more citations to scipy.stats tech improvements section as well.

\subsection*{Statistical distributions}
Version 1.0 of SciPy saw the addition of the energy distance algorithm in
\texttt{scipy.stats.energy\_distance}. Energy distance is used in a varity of applications ranging
from genetic analysis to multivariate independence. We also added the
first Wasserstein distance algorithm to the library in
\texttt{scipy.stats.wasserstein\_distance}. The Wasserstein distance is often
used in color digital image analysis.

We now also provide the cumulative distribution function of the multivariate
normal distribution, \\\texttt{scipy.stats.multivariate\_normal}, via the newly
associated \texttt{logcdf} and \texttt{cdf} methods.

Other recent additions to \texttt{scipy.stats} include the Argus distribution
in \texttt{scipy.stats.argus} (used in particle physics), a class for
generating a distribution from a histogram in
\texttt{scipy.stats.rv\_histogram}, an implementation of the multinomial
distribution in \texttt{scipy.stats.multinomial} (used for example in natural
language processing), a weighted Kendall's tau statistic algorithm in
\texttt{scipy.stats.weightedtau}, interquantile range handling in
\texttt{scipy.stats.iqr}, the Burr type XII distribution is available in
\texttt{scipy.stats.burr12}, the skew normal distribution has been implemented 
as \texttt{scipy.stats.skewnorm}, a trepzoidal continuous random variable
has been added in \texttt{scipy.stats.trapz}, and the matrix normal distribution
is now available in \texttt{scipy.stats.matrix\_normal}.

>>>>

\subsection*{Statistical distributions}
Version 1.0 of SciPy saw the addition of the energy distance algorithm in
\texttt{scipy.stats.energy\_distance}. Energy distance is used in a variety
of applications ranging from genetic analysis\cite{Hu2008DetectingIC} to 
multivariate independence\cite{szekely2009}. We also added the
first Wasserstein distance algorithm to the library in
\texttt{scipy.stats.wasserstein\_distance}. The Wasserstein distance is often
used in color digital image analysis \cite{192468}.

We now provide the cumulative distribution function of the multivariate
normal distribution, \\\texttt{scipy.stats.multivariate\_normal}, via the newly
associated \texttt{logcdf} and \texttt{cdf} methods. Other recent distributions 
added to \texttt{scipy.stats} include the Argus distribution
in \texttt{scipy.stats.argus} (used in particle physics\cite{ALBRECHT1990278}), a histogram-based
distribution in \texttt{scipy.stats.rv\_histogram}, the multinomial
distribution in \texttt{scipy.stats.multinomial} (used, for example, in natural
language processing\cite{Griffiths5228}), the Burr type XII distribution in
\texttt{scipy.stats.burr12}, the skew normal distribution 
in \texttt{scipy.stats.skewnorm}, the trapezoidal distribution in 
\texttt{scipy.stats.trapz}, and the matrix normal distribution
in \texttt{scipy.stats.matrix\_normal}.

There's also a new weighted Kendall's tau statistic algorithm in
\texttt{scipy.stats.weightedtau}, and interquantile range handling in
\texttt{scipy.stats.iqr}
